### 2017-10-04 1/exams/m1-practice.tex
Rename exam source.
Typos.

\begin{center}
\begin{tabular}{| c | c |}
  \hline
  Question & Points \\ \hline \hline
  1 & 10 \\ \hline
  2 & 10 \\ \hline
  3 & 10 \\ \hline
  4 & 20 \\ \hline
  5 & 10 \\ \hline
  6 & 20 \\ \hline \hline
  7 & 20 \\ \hline \hline
  Total: & 100\\
  \hline
\end{tabular}
\end{center}

@@

\begin{SaveVerbatim}{VerbEnv}
SOLUTION:
(posn-x (cond [(= (string-length "hi") 2) (make-posn 3 4)]
                  ^^^^^^^^^^^^^^^^^^^^                     -->[arith]
              [else (make-posn 8 0)]))
(posn-x (cond [(= 2 2) (make-posn 3 4)]
               ^^^^^^^                                     -->[arith]
              [else (make-posn 8 0)]))
(posn-x (cond [#true (make-posn 3 4)]
        ^^^^^^^^^^^^^^^^^^^^^^^^^^^^^       
              [else (make-posn 8 0)]))                     -->[arith]
              ^^^^^^^^^^^^^^^^^^^^^^^         
(posn-x (make-posn 3 4))              
^^^^^^^^^^^^^^^^^^^^^^^^                                   -->[arith]
3
\end{SaveVerbatim}

@@

\noindent
{\bf Problem 2 (10 points).}
%
The graphical text editor you developed in a recent assignment has
garned major attention by Bay-area venture capitalists who want to
base a start-up company around your editor.  They're ready to invest
to help you develop a full-featured prototype.  But before they write
a check, they want to make sure you can handle fancy operations for
expert text editor users.  They ask if you can implement a
\emph{transpose} operation, which will transpose the character to the
left of a cursor with the character to the right of the cursor.  To
satisfy your potential investors, you define the following function
for transposing characters at a given position in a string that has at
least 2 characters in it:
\begin{verbatim}
;; transpose : String Index -> String
;; Transpose characters at left and right of index i.
;; Assumes string has length >= 2 and 1<=i, i+1<=length.
(check-expect (transpose "ab" 1) "ba")
(check-expect (transpose "peice" 2) "piece")
(check-expect (transpose "student's" 8) "students'")
(define (transpose s i) ...)
\end{verbatim}

>>>>

\begin{center}
\begin{tabular}{| c | c |}
  \hline
  Question & Points \\ \hline \hline
  1 & 10 \\ \hline
  2 & 10 \\ \hline
  3 & 10 \\ \hline
  4 & 20 \\ \hline
  5 & 10 \\ \hline
  6 & 20 \\ \hline
  7 & 20 \\ \hline \hline
  Total: & 100\\
  \hline
\end{tabular}
\end{center}

@@

\begin{SaveVerbatim}{VerbEnv}
SOLUTION:
(posn-x (cond [(= (string-length "hi") 2) (make-posn 3 4)]
                  ^^^^^^^^^^^^^^^^^^^^                     -->[arith]
              [else (make-posn 8 0)]))
(posn-x (cond [(= 2 2) (make-posn 3 4)]
               ^^^^^^^                                     -->[arith]
              [else (make-posn 8 0)]))
(posn-x (cond [#true (make-posn 3 4)]
        ^^^^^^^^^^^^^^^^^^^^^^^^^^^^^       
              [else (make-posn 8 0)]))                     -->[cond]
              ^^^^^^^^^^^^^^^^^^^^^^^         
(posn-x (make-posn 3 4))              
^^^^^^^^^^^^^^^^^^^^^^^^                                   -->[arith]
3
\end{SaveVerbatim}

@@

\noindent
{\bf Problem 2 (10 points).}
%
The graphical text editor you developed in a recent assignment has
garnered major attention by Bay-area venture capitalists who want to
base a start-up company around your editor.  They're ready to invest
to help you develop a full-featured prototype.  But before they write
a check, they want to make sure you can handle fancy operations for
expert text editor users.  They ask if you can implement a
\emph{transpose} operation, which will transpose the character to the
left of a cursor with the character to the right of the cursor.  To
satisfy your potential investors, you define the following function
for transposing characters at a given position in a string that has at
least 2 characters in it:
\begin{verbatim}
;; transpose : String Index -> String
;; Transpose characters at left and right of index i.
;; Assumes string has length >= 2 and 1<=i, i+1<=length.
(check-expect (transpose "ab" 1) "ba")
(check-expect (transpose "peice" 2) "piece")
(check-expect (transpose "student's" 8) "students'")
(define (transpose s i) ...)
\end{verbatim}
